Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
OpenStack description
OpenStack corregido
results lammps

The first of them was {\it Montecarlo Multigpu} from NVIDIA SDK, launched with the default configuration ``scaling=weak'' which adjust the size of the problem depending on the number of accelerators.
The Figure~\ref{fig:mont-opt} depicts the options per second calculated by the application running on the scenarios of~\ref{fig:aws} and on the instances with local GPUs. 
We have removed the results of the Scenario~\ref{subfig:aws2} for clarity ought to they are exactly the same that the obtained from Scenario~\ref{subfig:aws3} up to 8 GPUs. 
In other words, we could state that the results until the 8th GPU would correspond to the Scenario~\ref{subfig:aws2} and thereafter to the Scenario~\ref{subfig:aws3}.
Hence, in this particular case, rCUDA (using remote GPUs) is performing better than CUDA (with its local GPUs) due to rCUDA loads the libraries when its daemon starts.
However, even with rCUDA we can see differences in the results between booth scenarios. We determined that the Scenario~\ref{subfig:aws1} could increase the throughput because
unlike the other setups the GPUs are not sharing the PCI bus with other devices, as it happens in the 4-GPU instances.

% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=\linewidth]{images/aws-mont2.png}
%   \caption{Montecarlo execution time}
%   \label{fig:mont-exe}
% \end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont1.png}
  \caption{Montecarlo options per second}
  \label{fig:mont-opt}
\end{figure}

Flexibility and economical expenses

>>>>

The first of them was {\it Montecarlo Multigpu} from NVIDIA SDK, launched with the default configuration ``scaling=weak'' which adjust the size of the problem depending on the number of accelerators.
The Figure~\ref{fig:mont-opt} depicts the options per second calculated by the application running on the scenarios of Figure~\ref{fig:aws} and on the instances with local GPUs. 
We have removed the results of the Scenario~\ref{subfig:aws2} for clarity ought to they are exactly the same that the obtained from Scenario~\ref{subfig:aws3} up to 8 GPUs. 
In other words, we could state that the results until the 8th GPU would correspond to the Scenario~\ref{subfig:aws2} and thereafter to the Scenario~\ref{subfig:aws3}.
Hence, in this particular case, rCUDA (using remote GPUs) is performing better than CUDA (with its local GPUs) due to rCUDA loads the libraries when its daemon starts.
However, even with rCUDA we can see differences in the results between booth scenarios. We determined that the Scenario~\ref{subfig:aws1} could increase the throughput because
unlike the other setups the GPUs are not sharing the PCI bus with other devices, as it happens in the 4-GPU instances.
% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=\linewidth]{images/aws-mont2.png}
%   \caption{Montecarlo execution time}
%   \label{fig:mont-exe}
% \end{figure}
\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont1.png}
  \caption{Montecarlo options per second}
  \label{fig:mont-opt}
\end{figure}

The other application, LAMMPS\footnote{\url{http://lammps.sandia.gov}}, is a classical molecular dynamics simulator that can be applied at the atomic, meso, or continuum scale. 
From the implementation perspective, this multi-process application employs at least one GPU to host its processes, but can benefit from the use of multiple GPUs.
The Figure shows that running this application using remote GPUs does not offer any advantage in front of original CUDA. 
Furthermore, for the execution on remote GPUs, can be seen a little difference between both networks, the ``High'' network performs worse than ``10 Gb'' network.
Thus, if we compare the results of a LAMMPS execution with a larger problem (see Figure), while CUDA performs better, the interesting point is the execution time on remote GPUs. 
They are almost the same even with different networks what means that the transfers are making the interconnection network the bottleneck, and enlarging the problem size
pays off the drawback of a slow network.

\begin{figure}[htb]
\centering
\subfigure[first]{%
\includegraphics[width=0.455\linewidth]{images/lammps100.png}
\label{subfig:lammps1}}
\quad
\subfigure[second]{%
\includegraphics[width=0.455\linewidth]{images/lammps2000.png}
\label{subfig:lammps2}}
\caption{Execution time of LAMMPS}
\label{fig:lammps}
\end{figure}

\subsection{Discussion}
Flexibility and economical expenses
